Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-24 ms.tex
added absolute zero level determination plot for Planck 2015 release
added 2015 version of full-sky temperature and optical depth results figure

@@

>>>>

\begin{figure}
\begin{center}
\epsfig{file=fig/zp_857.eps, width=3.4in}
\caption{\label{fig:fdsref} Scatter plot of FDS99-predicted 857 GHz thermal
dust emission versus \PLANCK~857 GHz observations, illustrating our absolute
zero level determination described in $\S$\ref{sec:zp_abs}.}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=fig/results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD
100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky
map of best-fit two-component 545 GHz optical depth.}
\end{center}
\end{figure*}
